### 2015-09-05 doc/article/article.tex
saving for other computer

\noindent Usually, we expect that the structures adopted by families of RNAs with similar functions such as Iron Response Elements (IREs) or transfer RNAs (tRNAs) are similar. To this end, our goal was to devise a method capable of finding similar structures within separate sets of suboptimal structures.

>>>>

\noindent Usually, we expect that the structures adopted by families of RNAs with similar functions such as Iron Response Elements (IREs) or transfer RNAs (tRNAs) to be similar. To this end, our goal was to devise a method capable of finding similar structures within separate sets of suboptimal structures.
